Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-24 robdml.tex
tex

We propose an additional loss function term to enforce such \emph{intra-class}
structure, as shown in \oo{Fig.~[].}
%
Specifically, the anchor $\va$ and its adversarial counterpart $\tilde{\va}$
are separated from the positve sample $\vp$ by reusing the triplet loss,
\ie,
%
\begin{equation}
	L_\text{ICS} = \lambda \cdot L_\text{T}(
	\va, \tilde{\va}, \vp; 0),
\end{equation}
%
where $\lambda$ is a constant hyper-parameter for controlling the importance
of this term.
%
$L_\text{ICS}$ can be added to the original loss function for adversarial training.

>>>>

We propose an additional loss function term to enforce such \emph{intra-class}
structure, as shown in \oo{Fig.~[].}
%
Specifically, the anchor $\va$ and its adversarial counterpart $\tilde{\va}$
are separated from the positve sample $\vp$ by reusing the triplet loss,
\ie,
%
\begin{equation}
	L_\text{ICS} = \lambda \cdot L_\text{T}(
	\va, \tilde{\va}, \vp; 0),
\end{equation}
%
where $\lambda$ is a constant hyper-parameter for controlling the importance
of this term, and the margin here is set as zero to avoid negative effect.
%
The $L_\text{ICS}$ penalty term can be appended to the loss function for
adversarial training.
